\Title

### 2023-01-20 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

In a review paper, we report experimental evidence for the presence of precise spiking motifs embedded in recordings from biological neural tissues~\cite{grimaldi_precise_2022}. These spatiotemporal patterns of neural activity can be a useful representation used by neurons to perform the computations needed to solve different cognitive tasks. In 1982, Abeles asked if the role of cortical neurons is whether to integrate synaptic inputs or rather to detect coincidences in temporal spiking motifs~\citep{abeles_role_1982}. While the first possibility favors the rate coding theory, the second highlights the function of temporal precision in the neural code. Since, numerous studies demonstrated the emergence of synchronicity in the activity within a neural population~\citep{riehle_spike_1997, davis_spontaneous_2021}, efficient encoding thanks to the use of spike latencies~\citep{perrinet_coding_2004, gollisch_rapid_2008} or precise timing in the auditory system~\citep{deweese_binary_2002, carr_circuit_1990}. All these findings, and more~\citep{bohte_evidence_2004}, highlight the importance of the temporal aspect of the neural code and suggest the existence of spatio-temporal spiking motifs in biological spike trains. In neuronal models, an efficient use or detection of these spatio-temporal motifs embedded in the spike train comes with the integration of heterogeneous delays~\citep{gutig_tempotron_2006, guise_bayesian_2014, zhang_supervised_2020}. Notably,~\citet{izhikevich_polychronization_2006} introduced the notion of the polychronous group as a repetitive motif of spikes defined by a subset of neurons with different, yet precise, relative spiking delays. This representation has a much greater information capacity in comparison to a firing-rate based neural coding approach through the variety of configurations and the possible coexistence of multiple superposed motifs.

>>>>

In a review paper, we report experimental evidence for the presence of precise spiking motifs embedded in recordings from biological neural tissues~\cite{grimaldi_precise_2022}. These spatiotemporal patterns of neural activity can be a useful representation used by neurons to perform the computations needed to solve different cognitive tasks. In 1982, Abeles asked if the role of cortical neurons is whether to integrate synaptic inputs or rather to detect coincidences in temporal spiking motifs~\citep{abeles_role_1982}. While the first possibility favors the rate coding theory, the second highlights the function of temporal precision in the neural code. Since, numerous studies demonstrated the emergence of synchronicity in the activity within a neural population~\citep{riehle_spike_1997, davis_spontaneous_2021}, efficient encoding thanks to the use of spike latencies~\citep{perrinet_coding_2004, gollisch_rapid_2008} or precise timing in the auditory system~\citep{deweese_binary_2002, carr_circuit_1990}. All these findings, and more~\citep{bohte_evidence_2004}, highlight the importance of the temporal aspect of the neural code and suggest the existence of spatio-temporal spiking motifs in biological spike trains. In neuronal models, an efficient use or detection of these spatio-temporal motifs embedded in the spike train comes with the integration of heterogeneous delays~\citep{guise_bayesian_2014, zhang_supervised_2020, nadafian}. Notably,~\citet{izhikevich_polychronization_2006} introduced the notion of the polychronous group as a repetitive motif of spikes defined by a subset of neurons with different, yet precise, relative spiking delays. This representation has a much greater information capacity in comparison to a firing-rate based neural coding approach through the variety of configurations and the possible coexistence of multiple superposed motifs.

This paper proposes additional experiments on a recent model of spiking neuron with heterogeneous synaptic delays.
